\documentclass{article}
\usepackage{graphicx}

\begin{document}

\title{MAGNETIC RECONNECTION IN SPACE AND LABORATORY PLASMAS AND IT’S IMPLICATION IN TOKAMAK PLASMA CONFINEMENT}
\author{Chase Johnson}

\maketitle

\begin{abstract}
Magnetic reconnection is the topological restructuring of magnetic field lines in high temperature plasmas.    The aim of this paper will be to describe the fundamental physics of magnetic reconnection and discuss the various MHD models to describe magnetic reconnection.  Magnetic reconnection as observed in both space plasmas and laboratory plasmas results in significant changes in kinetic and thermal properties of the plasma.  This inherently deteriorates the ability to confine plasma in the laboratory.  The second part of this paper will describe the fundamentals of saw-tooth instabilities triggering magnetic reconnection in tokamak plasma devices.  Due to the undesirable effects of magnetic reconnection in laboratory plasmas, several techniques have been developed to control sawtooth instabilities.  The efficacy of these techniques to include current drive schemes and ion population control will be discussed.
\end{abstract}


\section{Reconnection Defined}
Blank. 
\subsection{What is Reconnection}
Blank.
\subsection{Where Does Reconnection Occur}
Blank.
\subsection{Why is Reconnection Bad}
\section{References}
\begin{enumerate}
\item Aymar, R. \textit{et al} "The ITER design" 2001 \textit{Plasma Phys. Control Fusion} \textbf{44} 519.
\item Chapman, I. T. "Controlling sawtooth oscillations in tokamak plasmas" 2011 \textit{Plasma Phys. Control Fusion} \textbf{53} 1.
\item Chapman, I. T. \textit{et al} "Magnetic Reconnection Triggering Magnetohydrodynamic Instabilities during a Sawtooth Crash in a Tokamak Plasma" 2010 \textit{Phys. Rev. Lett.} \textbf{105} 255002.
\item Chapman, I. T. \textit{et al} "The physics of sawtooth stabilization" 2007 \textit{Plasma Phys. Control Fusion} \textbf{49} 12B.
\item Fridman, Alexander and Lawrence A. Kennedy,  \underline{Plasma Physics and Engineering},  Taylor and Francis Books, Inc., 2004.
\item Harry, John Earnest,  \underline{Introduction to Plasma Technology}, Wiley-VCH, 2010.
\item Hastie, R. J. "Sawtooth Instability in Tokamak Plasmas" 1998 \textit{Astrophysics and Space Science} \textbf{256} 177-204.
\item Priest, Eric,  \underline{Magnetohydrodynamics of the Sun},  Cambridge University Press, 2014.
\item Wagner, F. "A quarter-century of H-mode studies" 2007 \textit{Plasma Phys. Control. Fusion} \textbf{49} B12.
\item Wagner, F. "The Physics Basis of ITER Confinement" 2009 \textit{AIP Conf. Proc.} \textbf{1095} 31.
\item Yamada, Masaaki \textit{et al} "Investigation of magnetic reconnection during a sawtooth crash in a high‐temperature tokamak plasma" 1994 \textit{Phys. Plasmas} \textbf{1} 3269.
\item Yamada, Masaaki \textit{et al} "Magnetic Reconnection" 2010 \textit{Rev. Mod. Phys.} \textbf{82} 603.
\item Yun, G. S. \textit{et al} "Appearance and Dynamics of Helical Flux Tubes under Electron Cyclotron Resonance Heating in the Core of KSTAR Plasmas" 2012 \textit{Phys. Rev. Lett.} \textbf{109} 145003.
\end{enumerate}

\end{document}